---
title: "Setup DoD and ORIGINS plot Objects"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggpubr)
library(PairSeq)
library(data.table)
library(stringr)
library(dplyr)
library(janitor)
library(Biostrings)
library(pheatmap)

library(wesanderson)
library(treemapify)
library(ComplexHeatmap)
library(RColorBrewer)
library(viridis)
library(png)
library(ggplot2) # extra
library(cowplot)
library(ggrepel)

# PATH to our local project directory is not provided
setwd("[PATH to project folder]")
PLOT_DIR <- "plots"
```


# -------------------------------------


# DOD

# FIGURE 1
```{r}
load("pairseq/kmer_casepost.RData")
```


```{r}
dod_rpk  <- read.csv("rpk_tables/dod_rpk.csv",stringsAsFactors = F) 
epic_rpk <- read.csv("rpk_tables/epic_rpk.csv",stringsAsFactors = F) 
gfap_rpk <- read.csv("rpk_tables/gfap_rpk.csv",stringsAsFactors = F) 
pos_rpk  <- read.csv("rpk_tables/pos_rpk.csv",stringsAsFactors = F) 
pd_rpk   <- read.csv("rpk_tables/pd_rpk.csv",stringsAsFactors = F) 
```



```{r}
## Adding in the re-sequenced samples 
re_dod_rpk <- read.csv("rerun/dod_rpk.csv",stringsAsFactors = F) 
colnames(re_dod_rpk)<-gsub("_cgorigins","",colnames(re_dod_rpk))
missing <- setdiff(colnames(re_dod_rpk), colnames(dod_rpk))
dupes   <- intersect(colnames(re_dod_rpk), colnames(dod_rpk))
add_in  <- re_dod_rpk[,c("peptide", missing)]

## add in missing samples 
dod_rpk <- full_join(dod_rpk, add_in, by = "peptide")
```



```{r}
# Peptide gene name table
peptide_gene_map <- read.csv("metadata/peptide_gene_mapping.csv",stringsAsFactors = F) %>% clean_names()
colnames(peptide_gene_map)[1] <- "peptide"

#merged peptide map
merged_peptide_map <- read.csv("ref_oligos/merged_peptide_map.csv", stringsAsFactors = F)
merged_peptide_map <- merged_peptide_map %>% mutate(index = row_number())

# Load meta data
metadata      <- read.csv("metadata/list_with_plate_locations.csv",stringsAsFactors = F) %>% clean_names()
prepost       <- read.csv("metadata/Case_Control_Serum.csv", stringsAsFactors = F) %>% clean_names()
metadata$type <- str_replace_all(metadata$type,"\\ ","_")
still_missing <- setdiff(metadata$serum_id, colnames(dod_rpk))
```


```{r}
# 1b separate pre/post metadata 
collection <- c()
ser_yr <- c()

for (i in 1:nrow(metadata)){
  serID <- metadata$serum_id[i]
  if (serID %in% prepost$pre_serumid) {
    collection[i] <- "pre"
    ser_yr[i] <- prepost$pre_ser_yr[which(prepost$pre_serumid == serID)]
  } else if (serID %in% prepost$post_serumid) {
    collection[i] <- "post"
    ser_yr[i] <- prepost$post_ser_yr[which(prepost$post_serumid == serID)]    
  } else {
    collection[i] <- "NA"
    ser_yr[i] <- "NA"
  }
}

metadata <- cbind(metadata, collection, ser_yr)
metadata$ser_age <- metadata$ser_yr-metadata$year_birth
```


```{r}
# 2. Format Columns/subset data
col_names <- names(dod_rpk)
col_names <- str_replace_all(col_names,"\\.","_") 

cols_to_keep <- c()   
for (i in 2:length(col_names)) {
  sample    <- col_names[i]
  sample_id <- tstrsplit(sample,"_")[[1]] 
  metadata_sub <- metadata[metadata$serum_id %in% sample_id,]
  if(nrow(metadata_sub) == 0){next} 
  
  type <- metadata_sub$type
  collection <- as.character(metadata_sub$collection)
  studyid <- metadata_sub$studyid 
  sample_fmt <- paste(c(studyid, type, collection), collapse = "_")
  col_names[i] <- sample_fmt     
  
  cols_to_keep <- c(cols_to_keep,sample_fmt)
}

names(dod_rpk) <- col_names
```




```{r}
# PairSeq
beadnames <- names(pd_rpk)
bead_cols <- beadnames[grep("bead", beadnames)]
bead_rpk <- pd_rpk[, c("peptide", bead_cols)]

# 1. Merge both data sets (by peptide column)
df <- full_join(dod_rpk, epic_rpk, by = "peptide")
df <- full_join(df, pos_rpk, by = "peptide")
df <- full_join(df, gfap_rpk, by = "peptide")
df <- full_join(df, bead_rpk, by = "peptide")
df <- left_join(df, merged_peptide_map, by = "peptide")

#remove input dataframes
pos_cols <- names(pos_rpk)[2:6]
rm(dod_rpk, epic_rpk, gfap_rpk, pos_rpk, pd_rpk, bead_rpk)
```



```{r}
# 2. Create unique identifier column
df$peptide_id <- paste(df$gene, df$index,sep = "_")

#Replace NA values with 0
df[is.na(df)] <- 0
```


```{r}
# 3. Calculate Mean RPK

#get names 
all_names         <- names(df)
gfap_cols         <- all_names[grep("gfap",all_names)]
healthy_cols      <- all_names[grep("healthy",all_names)]
healthy_pre_cols  <- healthy_cols[grep("pre", healthy_cols)]
healthy_post_cols <- healthy_cols[grep("post", healthy_cols)]  
case_pre_cols     <- all_names[grep("Case_pre",all_names)]
case_post_cols    <- all_names[grep("Case_post",all_names)]
tbi_cols          <- all_names[grep("TBI",all_names)]
mig_cols          <- all_names[grep("Migraine",all_names)]
epic_csf_cols     <- all_names[grep("_csf",all_names)]
epic_serum_cols   <- all_names[grep("_serum",all_names)]
bead_cols         <- all_names[grep("bead",all_names)]

# Mean RPK and replace 0's with median value
df$mean_ref     <- apply(df[,c(healthy_cols)], 1, mean)     # Control group
hc_avg <- median(df$mean_ref)
df$mean_ref[df$mean_ref == 0] <- hc_avg

df$mean_disease <- apply(df[,c(case_post_cols)], 1, mean)   # Cases
case_avg <- median(df$mean_disease)
df$mean_disease[df$mean_disease == 0] <- case_avg

df$mean_beads   <- apply(df[,c(bead_cols)], 1, mean)        # Beads
bead_avg <- mean(df$mean_beads)
df$mean_beads[df$mean_beads == 0] <- bead_avg

df$sd_ref <-  apply(df[,c(healthy_cols)], 1, sd) 
```


```{r}
# 4. Calculate Fold Change
df_fc_ref    <- makeFCdf(df,
                         target_columns = healthy_cols,
                         mean_column    = "mean_ref",  onlyFC = T)
df_fc_disease <- makeFCdf(df,
                          target_columns = c(case_post_cols, case_pre_cols, tbi_cols, mig_cols, epic_csf_cols, epic_serum_cols, gfap_cols, pos_cols, bead_cols),
                          mean_column    = "mean_ref", onlyFC = T)

df_fc <- cbind(df_fc_ref,df_fc_disease)
rm(df_fc_disease, df_fc_ref)
```


```{r}
# 5. Calculate z score
fc_names <- names(df_fc)

gfap_fc_cols <- fc_names[grep("gfap",fc_names)]
gfap_z_cols  <- str_replace_all(gfap_fc_cols, "_FC","_Z")

healthy_fc_cols <- fc_names[grep("healthy",fc_names)]
healthy_z_cols  <- str_replace_all(healthy_fc_cols, "_FC","_Z")

healthy_pre_fc_cols <- healthy_fc_cols[grep("pre",healthy_fc_cols)]
healthy_pre_z_cols  <- str_replace_all(healthy_pre_fc_cols, "_FC","_Z")

healthy_post_fc_cols <- healthy_fc_cols[grep("post",healthy_fc_cols)]
healthy_post_z_cols  <- str_replace_all(healthy_post_fc_cols, "_FC","_Z")

case_pre_fc_cols <- fc_names[grep("Case_pre",fc_names)]
case_pre_z_cols  <- str_replace_all(case_pre_fc_cols, "_FC","_Z")

case_post_fc_cols <- fc_names[grep("Case_post",fc_names)]
case_post_z_cols  <- str_replace_all(case_post_fc_cols, "_FC","_Z")

tbi_fc_cols <- fc_names[grep("TBI",fc_names)]
tbi_z_cols  <- str_replace_all(tbi_fc_cols, "_FC","_Z")

mig_fc_cols <- fc_names[grep("Migraine",fc_names)]
mig_z_cols  <- str_replace_all(mig_fc_cols, "_FC","_Z")

epic_fc_csf_cols <- fc_names[grep("_csf",fc_names)]
epic_z_csf_cols  <- str_replace_all(epic_fc_csf_cols, "_FC","_Z")

epic_fc_serum_cols <- fc_names[grep("_serum",fc_names)]
epic_z_serum_cols  <- str_replace_all(epic_fc_serum_cols, "_FC","_Z")

pos_fc_cols <- paste0(pos_cols, "_FC")
pos_z_cols  <- str_replace_all(pos_fc_cols, "_FC","_Z")

bead_fc_cols <- paste0(bead_cols, "_FC")
bead_z_cols  <- str_replace_all(pos_fc_cols, "_FC","_Z")

df_z <- calcZscores(df_fc, target.samples = c(case_post_fc_cols, case_pre_fc_cols, tbi_fc_cols, mig_fc_cols, epic_fc_csf_cols, epic_fc_serum_cols, gfap_fc_cols, pos_fc_cols, healthy_fc_cols, bead_fc_cols), reference.samples = healthy_fc_cols)
names(df_z) <- str_replace_all(names(df_z), "_FC","_Z")
df_fc_z <- cbind(df, df_fc, df_z)
rm(df, df_fc, df_z)
```



```{r}
candidate_df_exp_fin_oldmeth <- candidate_df_fin 

candidate_df_exp_fin_oldmeth[is.na(candidate_df_exp_fin_oldmeth)] <- 0
candidate_df_exp_fin <- candidate_df_exp_fin_oldmeth[candidate_df_exp_fin_oldmeth$KmerOverlap > 0,]
candidate_df_exp_fin_singlet     <- candidate_df_exp_fin_oldmeth[candidate_df_exp_fin_oldmeth$KmerOverlap == 0,]
candidate_df_exp_fin_singlet_sub <- filterPeptides(candidate_df_exp_fin_singlet,list_of_samples = case_post_cols ,RPK_THRESH = 20,FC_THRESH = 100)

candidate_df_exp_fin <- rbind(candidate_df_exp_fin,candidate_df_exp_fin_singlet_sub)
```




## Make Filtered Dataframe
```{r}
tinydf <- candidate_df_exp_fin[c("peptide_id", case_pre_fc_cols, case_post_fc_cols, healthy_cols)]
tinydf <- tinydf %>% mutate(count_rich = rowSums(tinydf[, case_post_fc_cols[1:243]] > 10))
tinydf <- tinydf %>% filter(count_rich > 15)

top_peptides <- as.vector(tinydf$peptide_id)
```


```{r}
top_candidates <- candidate_df_exp_fin %>% filter(peptide_id %in% top_peptides)
top_candidates <- arrange(top_candidates, gene)

# peptide metadata for row annotation
top_pep_meta <- top_candidates[, c("peptide_id", "gene")]
peptide_id   <- top_pep_meta[, 1]
top_pep_meta <- top_pep_meta[ -1]
rownames(top_pep_meta) <- peptide_id
```


## Filter for Z-score columns
```{r}
tiny_z <- top_candidates[c("peptide_id", case_pre_z_cols, case_post_z_cols, healthy_pre_z_cols, healthy_post_z_cols )]

peptide <- tiny_z[, 1]
tiny_z  <- tiny_z[, -1]

rownames(tiny_z) <- peptide

z_metadata        <- metadata
z_metadata$sample <- with(metadata, paste0(studyid, "_", type, "_", collection, "_", "Z"))

z_metadata <- z_metadata[, c("sample", "type", "collection")]
rownames   <- z_metadata[, 1]
z_metadata <- z_metadata[, -1]
rownames(z_metadata) <- rownames
```


## Filter for FC columns
```{r}
tiny_fc <- top_candidates[c("peptide_id", case_pre_fc_cols, case_post_fc_cols, healthy_pre_fc_cols, healthy_post_fc_cols )]

peptide <- tiny_fc[, 1]
tiny_fc <- tiny_fc[, -1]
rownames(tiny_fc) <- peptide

fc_metadata        <- metadata
fc_metadata$sample <- with(metadata, paste0(studyid, "_", type, "_", collection, "_", "FC"))

fc_metadata <- fc_metadata[, c("sample", "type", "collection")]
rownames    <- fc_metadata[, 1]
fc_metadata <- fc_metadata[, -1]
rownames(fc_metadata) <- rownames
```


## Create Log10 FC dataframe
```{r}
tiny_logfc <- top_candidates[c("peptide_id", case_pre_fc_cols, case_post_fc_cols, healthy_pre_fc_cols, healthy_post_fc_cols )]

peptide    <- tiny_logfc[, 1]
tiny_logfc <- tiny_logfc[, -1]

rownames(tiny_logfc) <- peptide
tiny_logfc[tiny_logfc == 0] <- 1
tiny_logfc <- log10(tiny_logfc)

fc_metadata        <- metadata
fc_metadata$sample <- with(metadata, paste0(studyid, "_", type, "_", collection, "_", "FC"))

fc_metadata <- fc_metadata[, c("sample", "type", "collection")]
rownames    <- fc_metadata[, 1]
fc_metadata <- fc_metadata[, -1]
rownames(fc_metadata) <- rownames
```


# FIGURE 2


## Keep peptides with larmatope
```{r}
df_fc_z$sequence[1]

consensus_df       <- df_fc_z %>% filter(grepl("P[AS].[SGA]R[SN][RLHK]", sequence))
consensus_genelist <- consensus_df %>% select(peptide, gene, sequence, sequence, peptide_id)
```


## SAVE ENV
```{r}
env_fh <- "objects/TEMP_ENV_FIG1and2.RData"
save(list = ls(),file = env_fh)
```


# -------------------------------------

# ORIGINS

# FIGURE 3

## 1. Load obj and tables
```{r}
#CSF
load("pairseq/origins_csf_kmer.RData")
# Serum
load("pairseq/origins_serum_kmer.RData")
```



```{r}
# 1a. Load MEEBO RPK data frame
bead_rpk    <- read.csv("data_origins/beads_rpk.csv",stringsAsFactors = F) 
nid_rpk     <- read.csv("data_origins/nid_rpk.csv",stringsAsFactors = F) 
nybb_rpk    <- read.csv("data_origins/nybb_rpk.csv",stringsAsFactors = F) 
origins_rpk <- read.csv("data_origins/origins_rpk.csv",stringsAsFactors = F) 
gfap_rpk    <- read.csv("data_origins/gfap_rpk.csv",stringsAsFactors = F) 
```


## 2. Load and metadata
```{r}
# Load in bead metadata 
metadata <- read.csv("data_origins/ORIGINSEPICPatientSamples.csv",stringsAsFactors = F) %>% clean_names()
colnames(metadata)[1] <- "sample"

ond_ids  <- read.csv("data_origins/OND_ID_list.csv",stringsAsFactors = F)
ond      <- ond_ids$ID
ond      <- unique(ond)

# Get Sample Vectors
count_df <- metadata %>% filter(final_diagnosis == "MS_csf") 
ms_csf_cols <- count_df[, "sample"]

count_df <- metadata %>% filter(final_diagnosis == "MS_serum") 
ms_serum_cols <- count_df[, "sample"]

count_df <- metadata %>% filter(final_diagnosis == "OND_csf") 
ond_csf_cols <- count_df[, "sample"]

count_df <- metadata %>% filter(final_diagnosis == "OND_serum") 
ond_serum_cols <- count_df[, "sample"]

count_df <- metadata %>% filter(final_diagnosis == "Healthy_csf") 
healthy_csf_cols <- count_df[, "sample"]

count_df <- metadata %>% filter(final_diagnosis == "Healthy_serum") 
healthy_serum_cols <- count_df[, "sample"]

count_df <- metadata %>% filter(final_diagnosis == "CIS_serum") 
CIS_serum_cols <- count_df[, "sample"]

count_df <- metadata %>% filter(final_diagnosis == "CIS_csf") 
CIS_csf_cols <- count_df[, "sample"]

count_df <- metadata %>% filter(final_diagnosis ==  "RIS_serum") 
RIS_serum_cols <- count_df[, "sample"]

count_df <- metadata %>% filter(final_diagnosis == "RIS_csf") 
RIS_csf_cols <- count_df[, "sample"]

count_df <- metadata %>% filter(final_diagnosis ==  "Unknown_serum") 
unknown_serum_cols <- count_df[, "sample"]

count_df <- metadata %>% filter(final_diagnosis == "Unknown_csf") 
unknown_csf_cols <- count_df[, "sample"]

rm(count_df)
```


## 3.Get all relevant sample lists
```{r}
nid_cols  <- colnames(nid_rpk)[-1]
bead_cols <- colnames(bead_rpk)[-1]
nybb_cols <- colnames(nybb_rpk)[-1]
origins_cols <- colnames(origins_rpk)[-1]

#MS
origins_ms_csf_cols   <- paste0("X", ms_csf_cols, "_csf_cgorigins")
origins_ms_serum_cols <- paste0("X", ms_serum_cols, "_serum_cgorigins")
origins_ms_csf_cols   <- intersect(origins_cols, origins_ms_csf_cols)
origins_ms_serum_cols <- intersect(origins_cols, origins_ms_serum_cols)
origins_ms_cols       <- c(origins_ms_csf_cols, origins_ms_serum_cols)

#healthy controls
origins_healthy_csf_cols   <- c(paste0("X", healthy_csf_cols, "_csf_cgorigins"))
origins_healthy_serum_cols <- paste0("X", healthy_serum_cols, "_serum_cgorigins")
origins_healthy_csf_cols   <- intersect(origins_cols, origins_healthy_csf_cols)
origins_healthy_serum_cols <- intersect(origins_cols, origins_healthy_serum_cols)


#OND
origins_ond_csf_cols   <- c(paste0("X", ond_csf_cols, "_csf_cgorigins"))
origins_ond_serum_cols <- paste0("X", ond_serum_cols, "_serum_cgorigins")
origins_ond_csf_cols   <- intersect(origins_cols, origins_ond_csf_cols)
origins_ond_serum_cols <- intersect(origins_cols, origins_ond_serum_cols)

#CIS
origins_CIS_csf_cols   <- paste0("X", CIS_csf_cols, "_csf_cgorigins")
origins_CIS_serum_cols <- paste0("X", CIS_serum_cols, "_serum_cgorigins")
origins_CIS_csf_cols   <- intersect(origins_cols, origins_CIS_csf_cols)
origins_CIS_serum_cols <- intersect(origins_cols, origins_CIS_serum_cols)

origins_RIS_csf_cols   <- paste0("X", RIS_csf_cols, "_csf_cgorigins")
origins_RIS_serum_cols <- paste0("X", RIS_serum_cols, "_serum_cgorigins")
origins_RIS_csf_cols   <- intersect(origins_cols, origins_RIS_csf_cols)
origins_RIS_serum_cols <- intersect(origins_cols, origins_RIS_serum_cols)

origins_unknown_csf_cols   <- paste0("X", unknown_csf_cols, "_csf_cgorigins")
origins_unknown_serum_cols <- paste0("X", unknown_serum_cols, "_serum_cgorigins")
origins_unknown_csf_cols   <- intersect(origins_cols, origins_unknown_csf_cols)
origins_unknown_serum_cols <- intersect(origins_cols, origins_unknown_serum_cols)

all_origins <- c(origins_healthy_csf_cols, origins_healthy_serum_cols, origins_ond_csf_cols, origins_ond_serum_cols, origins_ms_csf_cols, origins_ms_serum_cols,
                 origins_CIS_csf_cols , origins_CIS_serum_cols, origins_RIS_csf_cols, origins_RIS_serum_cols,
                 origins_unknown_csf_cols,  origins_unknown_serum_cols)
mycraw <- setdiff(origins_cols, all_origins)

nid_csf_cols    <- nid_cols[grep("_csf_",nid_cols)]
ctrl_csf_cols   <- c(origins_healthy_csf_cols, origins_ond_csf_cols, nid_csf_cols )
ctrl_serum_cols <- c(nybb_cols, origins_healthy_serum_cols, origins_ond_serum_cols)
gfap_cols       <- c("GFAP_1_cgorigins", "GFAP_2_cgorigins", "GFAP_3_cgorigins", "GFAP_4_cgorigins")
```


## 4. Load and merge peptidome gene maps for plots
```{r}
# Peptide gene name table
peptide_gene_map <- read.csv("metadata/peptide_gene_mapping.csv",stringsAsFactors = F) %>% clean_names()
colnames(peptide_gene_map)[1] <- "peptide"

#merged peptide map
merged_peptide_map <- read.csv("ref_oligos/merged_peptide_map.csv", stringsAsFactors = F)
merged_peptide_map <- merged_peptide_map %>% mutate(index = row_number())
```


## 5. format origins df
```{r}
nid_rpk <- nid_rpk[, c("peptide", nid_csf_cols)]

# 1. Merge both data sets (by peptide column)
df <- full_join(origins_rpk, nid_rpk, by = "peptide")
df <- full_join(df, nybb_rpk, by = "peptide")
df <- full_join(df, bead_rpk, by = "peptide")
df <- full_join(df, gfap_rpk, by = "peptide")
df <- left_join(df, merged_peptide_map, by = "peptide")

#remove input dataframes
rm(origins_rpk, nid_rpk, bead_rpk, nybb_rpk, gfap_rpk)


# 2. Create unique identifier column
df$peptide_id <- paste(df$gene, df$index,sep = "_")

# Replace NA values with 0
df[is.na(df)] <- 0
any(is.na(df))
```


## 6. Setting up input dfs (CSF and Serum)

### a. mean calc
```{r}
# 3. Calculate Mean RPK

#Mean RPK and replace 0's with median value

##CSF
df$mean_csf_ref     <- apply(df[,c(ctrl_csf_cols)], 1, mean)     # Control group
hc_avg <- median(df$mean_csf_ref)
df$mean_csf_ref[df$mean_csf_ref == 0] <- hc_avg

df$mean_csf_disease <- apply(df[,c(origins_ms_csf_cols)], 1, mean)   # Cases
case_avg <- median(df$mean_csf_disease)
df$mean_csf_disease[df$mean_csf_disease == 0] <- case_avg

##Serum
df$mean_serum_ref     <- apply(df[,c(ctrl_serum_cols)], 1, mean)     # Control group
hc_avg <- median(df$mean_serum_ref)
df$mean_serum_ref[df$mean_serum_ref == 0] <- hc_avg

df$mean_serum_disease <- apply(df[,c(origins_ms_serum_cols)], 1, mean)   # Cases
case_avg <- median(df$mean_serum_disease)
df$mean_serum_disease[df$mean_serum_disease == 0] <- case_avg

##Beads
df$mean_beads   <- apply(df[,c(bead_cols)], 1, mean)        # Beads
bead_avg <- mean(df$mean_beads)
df$mean_beads[df$mean_beads == 0] <- bead_avg
```


### b. FC calc
```{r}
# 4. Calculate Fold Change

#CSF
df_fc_csf_ref    <- makeFCdf(df,
                         target_columns = ctrl_csf_cols,
                         mean_column    = "mean_csf_ref",  onlyFC = T)
df_fc_csf_disease <- makeFCdf(df,
                          target_columns = c(origins_ms_csf_cols),
                          mean_column    = "mean_csf_ref", onlyFC = T)

#Serum
df_fc_serum_ref    <- makeFCdf(df,
                         target_columns = ctrl_serum_cols,
                         mean_column    = "mean_serum_ref",  onlyFC = T)
df_fc_serum_disease <- makeFCdf(df,
                          target_columns = c(origins_ms_serum_cols, bead_cols),
                          mean_column    = "mean_serum_ref", onlyFC = T)


# Bind and delete
df_fc <- cbind(df_fc_csf_ref, df_fc_csf_disease, df_fc_serum_ref, df_fc_serum_disease)
rm(df_fc_csf_ref,df_fc_csf_disease, df_fc_serum_ref, df_fc_serum_disease)
```


### c. Z-score calc
```{r}
# 5. Calculate z score
ctrl_fc_csf_cols <- paste0(ctrl_csf_cols, "_FC")
ctrl_z_csf_cols <- str_replace_all(ctrl_fc_csf_cols, "_FC","_Z")

ctrl_fc_serum_cols <- paste0(ctrl_serum_cols, "_FC")
ctrl_z_serum_cols <- str_replace_all(ctrl_fc_serum_cols, "_FC","_Z")

origins_ms_fc_csf_cols <- paste0(origins_ms_csf_cols, "_FC")
origins_ms_z_csf_cols <- str_replace_all(origins_ms_fc_csf_cols, "_FC","_Z")

origins_ms_fc_serum_cols <- paste0(origins_ms_serum_cols, "_FC")
origins_ms_z_serum_cols <- str_replace_all(origins_ms_fc_serum_cols, "_FC","_Z")

bead_fc_cols <- paste0(bead_cols, "_FC")
bead_z_cols <- str_replace_all(bead_fc_cols, "_FC","_Z")

#csf
df_csf_z <- calcZscores(df_fc, target.samples = c(origins_ms_fc_csf_cols, ctrl_fc_csf_cols), reference.samples = ctrl_fc_csf_cols)
names(df_csf_z) <- str_replace_all(names(df_csf_z), "_FC","_Z")

#serum
df_serum_z <- calcZscores(df_fc, target.samples = c(origins_ms_fc_serum_cols, ctrl_fc_serum_cols, bead_fc_cols), reference.samples = ctrl_fc_serum_cols)
names(df_serum_z) <- str_replace_all(names(df_serum_z), "_FC","_Z")

#Bind and delete
df_z <- cbind(df_csf_z, df_serum_z)
rm(df_csf_z, df_serum_z)

#Stick the petide info back on
df_fc_z <- cbind(df, df_fc, df_z)

# remove input dataframes
rm(df, df_fc, df_z)
```

## 7. Filter CSF/Serum PairSeq hits

```{r}
# CSF
candidate_df_exp_fin_oldmeth <- candidate_df_csf_fin 

candidate_df_exp_fin_oldmeth[is.na(candidate_df_exp_fin_oldmeth)] <- 0
candidate_df_exp_fin <- candidate_df_exp_fin_oldmeth[candidate_df_exp_fin_oldmeth$KmerOverlap > 0,]
candidate_df_exp_fin_singlet     <- candidate_df_exp_fin_oldmeth[candidate_df_exp_fin_oldmeth$KmerOverlap == 0,]
candidate_df_exp_fin_singlet_sub <- filterPeptides(candidate_df_exp_fin_singlet,list_of_samples = origins_ms_csf_cols ,RPK_THRESH = 20,FC_THRESH = 100)

candidate_df_exp_csf_fin <- rbind(candidate_df_exp_fin,candidate_df_exp_fin_singlet_sub)


#serum
candidate_df_exp_fin_oldmeth <- candidate_df_serum_fin 
 
candidate_df_exp_fin_oldmeth[is.na(candidate_df_exp_fin_oldmeth)] <- 0
candidate_df_exp_fin <- candidate_df_exp_fin_oldmeth[candidate_df_exp_fin_oldmeth$KmerOverlap > 0,]
candidate_df_exp_fin_singlet     <- candidate_df_exp_fin_oldmeth[candidate_df_exp_fin_oldmeth$KmerOverlap == 0,]
candidate_df_exp_fin_singlet_sub <- filterPeptides(candidate_df_exp_fin_singlet,list_of_samples = origins_ms_serum_cols ,RPK_THRESH = 20,FC_THRESH = 100)
 
candidate_df_exp_serum_fin <- rbind(candidate_df_exp_fin,candidate_df_exp_fin_singlet_sub)

```


## ---CSF

## 8. CSF filters

### a. Make a filtered dataframe
```{r}
tinydf <- candidate_df_exp_csf_fin[c("peptide_id", origins_ms_fc_csf_cols, ctrl_fc_csf_cols, bead_fc_cols)]

tinydf <- tinydf %>% mutate(count_rich = rowSums(tinydf[, origins_ms_fc_csf_cols[1:141]] > 10))
tinydf <- tinydf %>% filter(count_rich > 10)
top_peptides <- as.vector(tinydf$peptide_id)
```


### b. filters for top peptides based on rowSum
```{r}
top_candidates <- candidate_df_exp_csf_fin %>% filter(peptide_id %in% top_peptides)
top_candidates <- arrange(top_candidates, gene)


#peptide metadata for row annotation
top_pep_meta <- top_candidates[, c("peptide_id", "gene")]
peptide_id <- top_pep_meta[, 1]
top_pep_meta <- top_pep_meta[ -1]
rownames(top_pep_meta) <- peptide_id
```


### c. make log10 FC dataframes
```{r}
tiny_logfc <- top_candidates[c("peptide_id", origins_ms_fc_csf_cols, ctrl_fc_csf_cols )]

peptide    <- tiny_logfc[, 1]
tiny_logfc <- tiny_logfc[, -1]

rownames(tiny_logfc) <- peptide
tiny_logfc[tiny_logfc == 0] <- 1
tiny_logfc <- log10(tiny_logfc)

fc_metadata1       <- as.data.frame(origins_ms_fc_csf_cols)
fc_metadata1$type  <- "MS"
fc_metadata1$fluid <- "csf"
colnames(fc_metadata1)[1] <- "sample" 

fc_metadata2       <- as.data.frame(ctrl_fc_csf_cols)
fc_metadata2$type  <- "OND"
fc_metadata2$fluid <- "csf"
colnames(fc_metadata2)[1] <- "sample" 

fc_metadata <- rbind(fc_metadata1, fc_metadata2)
rownames    <- fc_metadata[, 1]
fc_metadata <- fc_metadata[, -1]
rownames(fc_metadata) <- rownames
```


## ---Serum

## 9. Filter top candidates
```{r}
tinydf <- candidate_df_exp_serum_fin[c("peptide_id", origins_ms_fc_serum_cols, ctrl_fc_serum_cols, bead_fc_cols)]

target_serum_cols <- origins_ms_fc_serum_cols[1:length(origins_ms_fc_serum_cols)]

tinydf <- tinydf %>% mutate(count_rich = rowSums(tinydf[, target_serum_cols] > 10))
tinydf <- tinydf %>% filter(count_rich > 12)

top_peptides <- as.vector(tinydf$peptide_id)

## Organize top peptides
top_candidates <- candidate_df_exp_serum_fin %>% filter(peptide_id %in% top_peptides)
top_candidates <- arrange(top_candidates, gene)

# peptide metadata for row annotation
top_pep_meta <- top_candidates[, c("peptide_id", "gene")]
peptide_id   <- top_pep_meta[, 1]
top_pep_meta <- top_pep_meta[ -1]
rownames(top_pep_meta) <- peptide_id
```



## 10. Motif dataframes

### a. get motif dataframes
```{r}
df_fc_z$sequence[1]

consensus_df <- df_fc_z %>% filter(grepl("P[AS].[SGA]R[SN][RLHK]", sequence))
consensus_genelist <- consensus_df %>% select(peptide, gene, sequence, sequence, peptide_id)
```


### b. consensus totals
```{r}
long_consensus_serum_df <- consensus_df[c("peptide_id", origins_ms_serum_cols, ctrl_serum_cols )] %>% gather(key= sample, value = rpK, -peptide_id)  %>% group_by(sample) %>% summarise(sum_rpk = sum(rpK))


long_consensus_serum_df$def <- "NA"
for (i in 1:nrow(long_consensus_serum_df)){
  if(long_consensus_serum_df$sample[i] %in% origins_ms_serum_cols){
    long_consensus_serum_df$def[i] <- "MS"
  } else if(long_consensus_serum_df$sample[i] %in% ctrl_serum_cols){
    long_consensus_serum_df$def[i] <- "Control"
  }
}



long_consensus_csf_df <- consensus_df[c("peptide_id", origins_ms_csf_cols, ctrl_csf_cols )] %>% gather(key= sample, value = rpK, -peptide_id)  %>% group_by(sample) %>% summarise(sum_rpk = sum(rpK))

long_consensus_csf_df$def <- "NA"
for (i in 1:nrow(long_consensus_csf_df)){
  if(long_consensus_csf_df$sample[i] %in% origins_ms_csf_cols){
    long_consensus_csf_df$def[i] <- "MS"
  } else if(long_consensus_csf_df$sample[i] %in% ctrl_csf_cols){
    long_consensus_csf_df$def[i] <- "Control"
  }
}
```


# SAVE ENV

```{r}
env_fh <- "objects/TEMP_ENV_FIG3.RData"
save(list = ls(),file = env_fh)
```
