---
title: "Luminex - Process Data"
output: html_document
---


# START
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggpubr)
library(PairSeq)
library(data.table)
library(stringr)
library(dplyr)
library(janitor)
library(Biostrings)
library(pheatmap)
library(RColorBrewer)
library(viridis)
library(gplots)
library(wesanderson)
library(treemapify)
library(ComplexHeatmap)
library(png)
library(ggplot2) 
library(cowplot)
library(ggrepel)
library(plotly) 
library(uwot)
library(gridExtra)
library(seqinr)
library(DECIPHER)
library(Biostrings)
library(text.alignment)

ANTIGEN_LIST <- c("CLASRP","RIMS2","HFM","EBV BRRF2","KRT75","SRRM3","TRIO","BSA","CD320 epitope","Aspergillus","SRSF4","E. Coli","Pseudomonas","EBV ENV")

# PATH to our local project directory is not provided
setwd("[PATH to project folder]")

# Revised luminex data
luminex_data_dir <- "Luminex_Data/All_runs_with_repeats_included/Net_MFI_only"

# Diagnosis metadata
metadata <- read.csv("data_origins/ORIGINSEPICPatientSamples.csv",stringsAsFactors = F) %>% clean_names()

# Plot ENV RData from the manuscript
full_plot_env_fh <- "objects/ENV_PLOTS.RData"

# NIDs to keep 
nids_to_keep_metadata_fh     <- "resources/revisions_luminex/NIDs_to_keep_luminex_metadata.csv"
nids_to_keep_metadata        <- read.csv(nids_to_keep_metadata_fh,stringsAsFactors = F)
nids_to_keep_metadata$Sample <- str_replace_all(nids_to_keep_metadata$Sample," ","_")
nids_to_keep_metadata        <- nids_to_keep_metadata[nids_to_keep_metadata$metadata %in% "y",]

# Results Directories
PLOT_DIR   <- "plots"
TABLE_DIR  <- "Luminex_Data/processed_luminex_tables"

# Output object to save
output_origins_variables_fh <- file.path(TABLE_DIR,"origins_variables_for_plots.RData")
```


# FUNCTIONS

### loadMFIfile
```{r}
loadMFIfile <- function(file_name,dir_path) {
  batch <- str_replace_all(file_name,".csv","")
  batch <- str_replace_all(batch,".NetMFI","")
  
  mfi_df <- read.csv(file.path(dir_path,file_name),stringsAsFactors = F,check.names = F)
  mfi_df$batch <- batch
  
  return(mfi_df)
}
```

### collapseReplicatesLuminex
* Input should be BSA scaled luminex counts
```{r}
collapseReplicatesLuminex <- function(unique_id,lux_df_norm,antigen_cols,unique_id_col,plate_col) {
  lux_df_sub <- lux_df_norm[lux_df_norm[,unique_id_col] %in% unique_id,]
  lux_df_antigens <- lux_df_sub[,names(lux_df_sub) %in% antigen_cols]
  entry_df <- (colSums(lux_df_antigens)/nrow(lux_df_antigens)) %>% as.data.frame() %>% t() %>% as.data.frame()
  
  entry_df$Sample <- unique_id
  
  plate <- sort(unique(lux_df_sub[,plate_col]))
  if(length(plate) > 1){plate <- paste(plate,collapse = ":")}
  entry_df$Plate <- plate
  
  # re-order
  entry_df <- entry_df[,c("Sample","Plate",antigen_cols)]
  
  return(entry_df)
}
```

# -------------------------------------

# COMBINE ALL NEW LUMINEX DATA

* Prior to running this code, CSVs were pre-processed manaully to get MFI data only

# 1. Merge all CSVs
```{r}
file_list <- list.files(luminex_data_dir) %>% as.list()
df_list   <- lapply(file_list, loadMFIfile,dir_path=luminex_data_dir)
lux_df    <- do.call("rbind",df_list)
```

# 2. Add info columns

### a. Plate
```{r}
# Plate columns
plate_col <- lux_df$batch
plate_col <- tstrsplit(plate_col,"_")[[1]]
plate_col <- str_replace_all(plate_col,"updated","")
plate_col[plate_col %in% "rerun"] <- "MixedPlate"
plate_col[plate_col %in% "JP"] <- "ExtraPlate"
lux_df$plate <- plate_col
```

### b. Sample formatted and Unique ID
```{r}
# Formatted Samples
sample_fmt_col <- lux_df$Sample
sample_fmt_col <- str_replace_all(sample_fmt_col," ","_")
lux_df$sample_fmt <- sample_fmt_col

# Unique ID to separate replicates
lux_df$unique_id  <- tstrsplit(lux_df$sample_fmt,"_rep")[[1]]

replicate_summary <- table(lux_df$unique_id) %>% as.data.frame()
names(replicate_summary) <- c("unique_id","count")
```

# 3. Omit first run samples that were repeated
```{r}
lux_df$index <- as.character(1:nrow(lux_df))

repeat_samples <- lux_df$sample_fmt[grep("repeat",lux_df$sample_fmt)]
uni_ids_with_repeats <- lux_df[lux_df$sample_fmt %in% repeat_samples,"unique_id"] %>% unique()

replicate_summary_w_rep <- replicate_summary[replicate_summary$unique_id %in% uni_ids_with_repeats,]

ids_to_check <- replicate_summary_w_rep[replicate_summary_w_rep$count !=2,"unique_id"] %>% as.character()

rows_to_omit <- c()
for (uni_id in ids_to_check) {
  pt_sub <- lux_df[lux_df$unique_id %in% uni_id,]
  target_samples <- pt_sub$sample_fmt[grep("repeat",pt_sub$sample_fmt)]
  omit_samples   <- pt_sub$sample_fmt[! pt_sub$sample_fmt %in% target_samples]
  rows_to_omit <- c(rows_to_omit,omit_samples)
}
lux_df <- lux_df[! lux_df$sample_fmt %in% rows_to_omit,]
```

# 4. BSA normalize
* Divide all antigens by BSA
```{r}
lux_df_norm <- lux_df

bsa_values <- lux_df_norm$BSA

for (a in ANTIGEN_LIST) {
  lux_df_norm[,a] <- lux_df_norm[,a] / bsa_values
}
```


# 5. Collapse duplicates
* average replicates
* Take log of average values
* Sum MFI and avg MFI are done across all antigens post averaging replicates. Log scaling is done after.
```{r}
id_list <- unique(lux_df_norm$unique_id) %>% as.list()

df_norm_list <- lapply(id_list, collapseReplicatesLuminex,lux_df_norm=lux_df_norm,
                       antigen_cols=ANTIGEN_LIST,
                       unique_id_col="unique_id",plate_col="plate")

lux_df_fin <- do.call("rbind",df_norm_list)
```

# 6. Sum/Avg MFI 

### a. autoantigens
```{r}
lux_df_fin$pep_sum_mfi <- lux_df_fin$SRSF4 + lux_df_fin$KRT75 + lux_df_fin$RIMS2 + lux_df_fin$TRIO + lux_df_fin$CLASRP + lux_df_fin$SRRM3

lux_df_fin$pep_sum_mfi_no_SRRM3 <- lux_df_fin$SRSF4 + lux_df_fin$KRT75 + lux_df_fin$RIMS2 + lux_df_fin$TRIO + lux_df_fin$CLASRP

lux_df_fin$pep_mean_mfi <- (lux_df_fin$SRSF4 + lux_df_fin$KRT75 + lux_df_fin$RIMS2 + lux_df_fin$TRIO + lux_df_fin$CLASRP + lux_df_fin$SRRM3) / 6
```

### b. pathogens
```{r}
lux_df_fin$pep_sum_mfi_pathogens <- lux_df_fin$`EBV BRRF2` + lux_df_fin$`EBV ENV` + lux_df_fin$Aspergillus + lux_df_fin$`E. Coli` + lux_df_fin$Pseudomonas + lux_df_fin$HFM

lux_df_fin$pep_mean_mfi_pathogens <- (lux_df_fin$`EBV BRRF2` + lux_df_fin$`EBV ENV` + lux_df_fin$Aspergillus + lux_df_fin$`E. Coli` + lux_df_fin$Pseudomonas + lux_df_fin$HFM) / 6
```


# 7. Log Scale
```{r}
lux_df_fin_log <- lux_df_fin

for (a in c(ANTIGEN_LIST,"pep_sum_mfi","pep_sum_mfi_no_SRRM3","pep_mean_mfi","pep_sum_mfi_pathogens","pep_mean_mfi_pathogens")) {
  lux_df_fin_log[,a] <- log((lux_df_fin_log[,a] + 1))
}
```

# 6. Write TSVs
```{r}
write.table(lux_df,file = file.path(TABLE_DIR,"Full_Luminex_revised_df.unprocessed.tsv"),sep = "\t",quote = F,row.names = F)

write.table(lux_df_fin,file = file.path(TABLE_DIR,"Luminex_revised_processed_df.tsv"),sep = "\t",quote = F,row.names = F)

write.table(lux_df_fin_log,file = file.path(TABLE_DIR,"Luminex_revised_processed_df.log.tsv"),sep = "\t",quote = F,row.names = F)
```


# -------------------------------------

# PREPARE FOR PLOT

# 1. filter for samples in the study
```{r}
lux_df_plot <- lux_df_fin_log

# Remove extra plate but keep select NIDs
lux_df_plot_nid <- lux_df_plot[lux_df_plot$Plate %in% "ExtraPlate",]
nids_to_keep_metadata$SampleFormatted <- tstrsplit(nids_to_keep_metadata$Sample,"_rep")[[1]]

# List samples to keep in plot dataframe
samples_to_keep_nid <- lux_df_plot_nid$Sample[lux_df_plot_nid$Sample %in% nids_to_keep_metadata$SampleFormatted]
samples_to_keep <- lux_df_plot[! lux_df_plot$Plate %in% "ExtraPlate","Sample"]

lux_df_plot     <- lux_df_plot[lux_df_plot$Sample %in% c(samples_to_keep_nid,samples_to_keep),]

# Remove plate controls
plate_cntrls <- lux_df_plot$Sample[grep("Plate|Control|Secondary",lux_df_plot$Sample)]
lux_df_plot         <- lux_df_plot[! lux_df_plot$Sample %in% plate_cntrls,]
lux_df_plot$Patient <- tstrsplit(lux_df_plot$Sample,"_")[[1]]
lux_df_plot$fluid     <- tstrsplit(lux_df_plot$Sample,"_")[[2]]
lux_df_plot$fluid[lux_df_plot$fluid %in% c("1:1","CSF")] <- "csf"
```

# 2. Add in diagnosis
```{r}
ond_ids  <- read.csv("data_origins/OND_ID_list.csv",stringsAsFactors = F)
ond      <- ond_ids$ID
ond      <- unique(ond)

colnames(metadata)[1] <- "Patient"
bare_bones <- metadata %>% select(Patient, disease_status,final_diagnosis, epicid)

# Keep track of non-overlapping IDs
missing_ids <- lux_df_plot$Patient[! lux_df_plot$Patient %in% bare_bones$Patient] %>% unique()

lux_df_plot <- left_join(lux_df_plot, bare_bones, by = "Patient")

# Merge final diagnosis with fluid
lux_df_plot$final_diagnosis <- paste(lux_df_plot$final_diagnosis, lux_df_plot$fluid, sep = "_")
```

# 3. Create Long df

### a. plot df
```{r}
anitgen_list_filt <- ANTIGEN_LIST[! ANTIGEN_LIST %in% c("BSA","CD320 epitope")]

lux_df_long <- lux_df_plot[, c("Patient", "final_diagnosis",anitgen_list_filt)] %>% gather(key = "bead", value = "mfi", -Patient, - final_diagnosis)
```

### b. NID
```{r}
lux_df_long_nid <- lux_df_plot_nid[, c("Sample",anitgen_list_filt)] %>% gather(key = "bead", value = "mfi", -Sample)
```

# 4. Write TSVs

### a. Plot Dataframes
```{r}
write.table(lux_df_plot,file = file.path(TABLE_DIR,"plot_df_Luminex_revised_processed.tsv"),sep = "\t",quote = F,row.names = F)

write.table(lux_df_long,file = file.path(TABLE_DIR,"long_plot_df_Luminex_revised_processed.tsv"),sep = "\t",quote = F,row.names = F)
```

### b. NID
```{r}
write.table(lux_df_plot_nid,file = file.path(TABLE_DIR,"NID_plot_df_Luminex_revised_processed.tsv"),sep = "\t",quote = F,row.names = F)

write.table(lux_df_long_nid,file = file.path(TABLE_DIR,"NID_long_plot_df_Luminex_revised_processed.tsv"),sep = "\t",quote = F,row.names = F)
```

# -------------------------------------

# GET ORIGINS VARIABLE TO KEEP FOR PLOTS

* This does not account for the fact that one patient was later diagnosed with MS

# 1. Load full Plot ENV
```{r}
load(full_plot_env_fh)
```

# 3. SAVE
```{r}
save(samples_origins_ms_fig3b,patients_origins_cluster,pts_to_omit,
     samples_fig3a,pt_ms_fig3a,samples_ctrl_fig3b,pt_ctrl_fig3b,file = output_origins_variables_fh)
```

